---
title: "Homework 0"
author: Karina L. Bellavia
format: html
---


# How do you solve a quadratic equation at x = 0?

## Introduction

The basic formula for the quadratic formula is:

$$f(x) = ax^2 + bx + c$$

``` {r}
#| echo: false

a <- 1
b <- 3
c <- 2

D <- b^2 - 4*a*c
```

In our case, our numerical coefficients are:

a = `r a`

b = `r b`

c = `r c`

We can now fill in the quadratic equation:

$$f(x) = `r a`x^2 + `r b`x + `r c`$$

## Step 1: Solve for the discriminant

First, we must calculate the discriminant. We can do this by using the formula: $$b^2 - 4ac$$A positive discriminant indicates there are 2 real solutions, a discriminant of zero indicates there is 1 real solution, and a negative discriminant indicates there are zero real solutions.

## Step 2: Solve!

If we have a positive discriminant or a discriminant equal to zero, we can solve using the quadratic formula: $$x = -b ± \frac{\sqrt{b^2 - 4ac}}{2a}$$

If the discriminant equals zero, we have two identical solutions. Therefore, it does not matter whether we we 

## Now, let's solve our quadratic equation.

Here is the discriminant for our equation: `r D`

```{r}
#| echo: false
#| output: false
w <- if (D > 0) {
  s1 <- (-b + sqrt(b^2 - 4*a*c)) / (2*a)
  s2 <- (-b - sqrt(b^2 - 4*a*c)) / (2*a) 
  print(paste(sprintf("there are two solutions! The solutions are: %d, %d", s1, s2)))
} else if(D == 0) {
  s1 <- (-b + sqrt(b^2 - 4*a*c)) / (2*a)
  print(paste(sprintf("there is one solution! The solution is: %d", s1)))
} else {
    print(paste("there are no solutions.")) }
```

Given our discriminant, `r w`

## Graph of the Quadratic Equation

$$f(x) = `r a`x^2 + `r b`x + `r c`$$
```{r}
#| echo: false
invisible({
x <- seq(-5, 5, length  = 300)
plot(x, a*x^2 + b*x + c, type = "l", ylab = "y") +
abline(h = 0, lty = 2)})
```
